Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-05 Paper/assa.tex
boltzmann ...

\label{sub:gsa}
Consider a function $f(\xi_1, \xi_2, \ldots, \xi_\Np)$. 
Whereas the active subspace framework described above not make any assumptions
about statistical independence of the input parameters $\xi_i$, $i = 1, \ldots, \Np$, 
the classical 
framework of variance based sensitivity analysis~\cite{Sobol:2001, Saltelli:2010} assumes the input
parameters are statistically independent. While extensions to the cases 
of correlated inputs exist, we limit the discussion in this section to the
case of random inputs that are statistically independent and are 
either uniformly distributed or
distributed according to a Boltzmann probability distribution~\alennote{Explain what this
is, and give a reference}.

@@

It was shown in~\cite{Lamboni:2013} that the total Sobol' 
index $T_i(f)$ can be bounded in terms of $\nu_i(f)$:
\begin{equation}\label{equ:sobol_bound}
T_i(f) \leq \frac{C_i}{\V(f)}\nu_i(f), \quad i = 1, \ldots, \Np,
\end{equation}
where for each $i$, $C_i$ is an appropriate \emph{Poincar\'{e}} constant.
This provides a strong theoretical basis for using DGSMs to identify 
unimportant inputs. Moreover, 
in~\cite{Vohra:2018} we introduced the normalized screening metric
\[
   \tilde{\nu}_i(f) = \frac{C_i \nu_i(f)}{\sum_{i=1}^\Np C_i \nu_i(f)},
\]
for detecting unimportant input parameters. 
Note that if $\xi_i$ are iid, the $C_i$'s will cancel and the normalized screening
metric reduces to 
\[
    \tilde{\nu}_i(f) = \frac{\nu_i(f)}{\sum_{i=1}^\Np \nu_i(f)} 
      = \frac{\vec{e}_i^T \mat{C} \vec{e}_i}{\trace(\mat{C})} 
      = \frac{\sum_{k=1}^\Np \lambda_k \ip{\vec{e}_i}{\vec{u}_k}^2}{\sum_{k = 1}^\Np \lambda_k}.
\]

>>>>

\label{sub:gsa}
Consider a function $f(\xi_1, \xi_2, \ldots, \xi_\Np)$. 
Whereas the active subspace framework described above not make any assumptions
about statistical independence of the input parameters $\xi_i$, $i = 1, \ldots, \Np$, 
the classical 
framework of variance based sensitivity analysis~\cite{Sobol:2001, Saltelli:2010} assumes the input
parameters are statistically independent. While extensions to the cases 
of correlated inputs exist, we limit the discussion in this section to the
case of random inputs that are statistically independent and are 
either uniformly distributed or
distributed according to a Boltzmann probability distribution.
Note that a measure $\mu$
on $\R$ is referred to as a Boltzmann measure if it is 
absolutely continuous with respect to the Lebesgue measure  
and admits a density  of the form $\pi(x) = C \exp\{-V(x)\}$,
where $V$ is a continuous function and $C$ a normalization 
constant~\cite{Lamboni:2013}.

@@

It was shown in~\cite{Lamboni:2013} that the total Sobol' 
index $T_i(f)$ can be bounded in terms of $\nu_i(f)$:
\begin{equation}\label{equ:sobol_bound}
T_i(f) \leq \frac{C_i}{\V(f)}\nu_i(f), \quad i = 1, \ldots, \Np,
\end{equation}
where for each $i$, $C_i$ is an appropriate \emph{Poincar\'{e}} constant
that depends on the distribution of $\xi_i$.
This provides a strong theoretical basis for using DGSMs to identify 
unimportant inputs. Moreover, 
in~\cite{Vohra:2018} we introduced the normalized screening metric
\[
   \tilde{\nu}_i(f) = \frac{C_i \nu_i(f)}{\sum_{i=1}^\Np C_i \nu_i(f)},
\]
for detecting unimportant input parameters. 
Note that if $\xi_i$ are iid, the $C_i$'s will cancel and the normalized screening
metric reduces to 
\[
    \tilde{\nu}_i(f) = \frac{\nu_i(f)}{\sum_{i=1}^\Np \nu_i(f)} 
      = \frac{\vec{e}_i^T \mat{C} \vec{e}_i}{\trace(\mat{C})} 
      = \frac{\sum_{k=1}^\Np \lambda_k \ip{\vec{e}_i}{\vec{u}_k}^2}{\sum_{k = 1}^\Np \lambda_k}.
\]
